### 2017-02-16 thesis/results/results2.tex
tmp commit

(add heatmaps of other data as well? or maybe in appendix)

@@

To confirm that the obesity associated metagenes were not related to any of the biological pathway signatures from the \citet{Gatza2010a} study, linear models were created to predict the obesity metagene scores with the pathway metagene scores.
If any of the pathway metagenes were significant in the linear model, this provides a strong evidence that the significant pathways in the model were related to the obesity metagene.
% TODO: start from here

>>>>

(add heatmaps of other data (Creighton/FM/Cris) as well? or maybe in appendix)

@@

To confirm that the obesity associated metagenes were not related to any of the biological pathway signatures from the \citet{Gatza2010a} study, linear models were created to predict the obesity metagene scores with the pathway metagene scores.
If any of the pathway metagenes were significant in the linear model, this provided evidence that the significant pathways in the linear model were related to the obesity metagene.
Since most of the obesity metagenes were found in Creighton's data set and only Creighton's and Cris' data sets had \gls{bmi}/\gls{bmi} status information for the samples, Cris' data set was used as the training data set to create linear models for obesity metagene score prediction.

Metagene scores used for the construction of linear models were generated from the application of the transformation matrices derived from Gatza's data (from \cref{sec:pathway_associated_metagenes_and_obesity_associated_metagenes}) to \gls{rma}-normalised Cris' data.
For each of the obesity metagenes identified, seven linear models were created: \gls{bmi}-only, \gls{bmi} status-only, \gls{bmi} and \gls{bmi} status, pathway metagenes-only, and all of the combinations of pathway metagenes with \gls{bmi} and/or \gls{bmi} status.
